My Past Work

### 2025-01-24 about.qmd
Update
2025 Update

**National University of Singapore**\
*Bachelor of Social Sciences \[Hons.\], Communications New Media / Sociology, Social Sciences* <br> Aug 2022 - Present

@@

**Product Specialist**\
*Apple South Asia* <br> Aug 2023 - Present · 4 mos

@@

**Marketing Research Intern**\
*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos

@@

>>>>

**National University of Singapore**\
*Bachelor of Social Sciences \[Hons.\], Interactive Media Development/ Sociology, Social Sciences* <br> Aug 2022 - Present

@@

**Specialist**\
*Apple South Asia Pte. Ltd.* <br> Aug 2023 - Present

@@

**Marketing Intern**\
*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos

@@

## Contact Details

For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com

### 2025-01-24 articles.qmd
2025 Update

<summary> Singapore's Public Housing Affordability <br> <br>  <p> In Singapore, housing affordability has been an increasing worry for future Singaporeans. However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012). Read more here... </p> </summary>

@@

While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.

@@

Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future. This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.

@@

The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.

@@

According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue. The table above provides an outline of the housing prices in Singapore. Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.

@@

For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230. While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.

@@

Imagine you and your sponse are looking to start a family. Now that we've a glimpse into the affordability of homes in Singapore, do you think you can comfortably own your own home when the time comes? Let's dive into real data and discuss this critical issue further.

@@

Before moving on to the deeper analysis, let us understand how the overall prices have increased from 1990 to 2022. While the general increase in prices overtime aligns with economic growth, the rate of the surge from 1990 to 2022 is alarming.

@@

One may argue that the increment is a sign of prospering economy, on the other side, it also rings alarm bells in terms of overall affordability. Now let's examine the graph below:

@@

The graph above illustrates a significant steepening in the slopes of average resale prices in Singapore from 1990 to 2022 - indicating the exorbitant increase of prices across all flat types. The steeper slope in 2022 shows a more prominent price escalation as compared to 1990's. This is can be an indication increasing pressure on affordability and financial stretch for home ownership.

@@

Notice that on the graph, there is a worrying widening price gap between each successive flat type, with the difference in average prices from one flat type to the next becoming more distinct. For example, the price jump from a 3-room to a 4-room for both 1990 and 2022, may point towards a growing demand for a larger home. Larger home, bigger family right?

@@

With that, we can understand that the widening gap of prices could create a cost burden for upgraders seeking more specious accommodations for a bigger family. The growing gap in prices shows that planning for home ownership is extremely crucial to prevent any buyers' remorse.

@@

Now let's look at the price increment individually for both years, compared with the same flat type. The graph presented shows a great difference for a 4-room flat between 1990 and 2022.

@@

The year 1990 with an average price of SGD\$81,525 and 2022 with an average price of SGD\$525,092, represented by green and orange respectively. In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022!

@@

As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options. Additionally, the graph suggests that the real estate market has become increasingly segmented. Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020).

@@

For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019). To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market.

@@

While a price increment can potentially indicate a critical issue with affordability, it is also important to access where the increase is still within the "safe" median range. However, in the box plot below, we can see how the presence of outliers underscores the significant and unprecedented price increase.

@@

Furthermore, across the other flat types, there is an increasing number of outliers beyond the upper whiskers of the box plots for 2022. While this can suggest a substantial market growth, it can also reflect the high number of exceptional cases where resale prices are charging a even higher premium, exceeding the median trends - which is already high.

@@

Now, that we have clearly seen the high prices Singaporean are willing to pay for their dream home, are there other factors that can be attributed to the price increase? Next, we will explore if the remaining lease left or the location of the flat affect the resale price.

@@

To lower the cost burden for flat upgraders, some may consider purchasing a flat with a lower remaining lease. However, is there a correlation between the remaining lease and the cost of a resale flat in 1990 and 2022?

@@

As we look and examine into the numbers, it becomes clear that patterns have shifted from 1990 to 2022. Here, we will be comparing the data from these two distinct years. Now let's look at the scatterplot below. Pay attention to the red line, what does it tell you?

@@

In 1990, the line suggested a clear trend: where a longer remaining lease often correlated with a higher resale price. The regression line showed a noticeable upward slope; decently steep actually. This would indicate that the longer the remaining lease, the higher the resale price of the flat, which makes sense at the time where buyers could reside in the flat without facing any lease expiration issue in the future.

@@

However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep. This suggests that the remaining lease period is not as strong an indicator as it was in 1990. Also, the data points are more spread out , indicating a high variance in resale prices. We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.

@@

Put yourself in the shoes of the buyer, would you get a house with longer remaining lease, but with everything else an hour away or a shorter remaining lease with everything else a stone's throw away?

@@

The answer is not merely a matter of counting the years on a lease. So far, none of the HDB flats have seen their lease expired. So no one knows what really happens after that. Buying your own home is also about weighing the value or time and quality of your daily life. After all, what is a good extended lease if it comes at an expense of your convenience and time? Now, we will look into another important factor: The Estate

@@

We can agree that price is an important consideration for purchasing a home. Have you figured out where to live? Do you want to live close to your parents in the same estate? Or do you have a preferred school you would like to send your future children too? Now, we will examine if the estate affects the price of the resale flat. We will also determine which estate tends to be more costly or cheaper to settle down.

@@

Now, let's explore the violin plot on the interactive dashboard. For visualisation, we will use Bukit Timah and Punggol. According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is known for it access to many well sought after educational institutes such as Hwa Chong Institutions, National Junior College and Raffles Girls' Primary School, making it one of the most popular estate.

@@

[Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate. It is slowly becoming popular with younger couples due to its modern amenities and promising development plans. The town is being developed with a vision to be eco-friendly, sustainable while providing trendy lifestyle hubs that cater to all age groups.

@@

That being said, let's analyse the violin plot. We can observe the wider distribution of resale prices, with a more pronounced upper tail. This would indicate there are a larger variety of flats, but also a substantial market for high-end luxury flats.

On the flip side, Punggol has a narrower but dense concentration of price, indicating a more concrete (or less variation) in resale prices. Now, let's interact with the plot, select your dream estates and explore the price variations! Oh and just in case, I'll put the MRT Map here for reference!

@@

Now, if we were to deduce on which is the best place to settle down based on what we have gathered, the decision really depends on what you value the most. For instance, if you value tranquility and a sea view, Punggol would be great.

@@

However, if you would like be in close proximity of prestigious schools, *(all schools are good schools - but let's not get into that for now)* then Bukit Timah might be the best choice for you! The visualisation does not only tell us about the prices, but also a reflection of lifestyle, and the long-term family vision for you and your spouse!

@@

Year-on-year, the prices of resale HDB flats have seen a continuous rise, reflecting in a growing demand of housing solutions in Singapore. However, this brings concerns to many Singaporeans, especially younger couples intending to start a family, as they struggle with affordability and availability issues.

@@

According to recent reports, analysts indicated that prices of resale flats are expected to rise moderately for the remainder of 2023 (CNA, 2023). While cooling measures have taken place to control the prices, the growth in the third quarter of 2023 was due to price resistance setting in amid inflationary and affordability concerns.

@@

You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right! But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down? Certainly, the choice to ballot for a BTO flat, despite its lower cost and readily available grants, requires risk-taking and uncertainties.

@@

Therefore, this analysis could provide a thoughtful evaluation of the need for immediate housing against the potential delays and challenges of the BTO process. For now, all we can do is leverage on the available grants and ensure that we spend on what we can afford.

@@

<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p> This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance. Read more here... </p> </summary>

@@

<p style="text-align: right;"> Friday, 10 May 2024</p>

@@

<p> Jeremy’s desistance from deviance can be explored through Hirschi’s (1969) Social Bond Theory. Kotlaja and Meier (2018), cited Hirschi (1969), mentioned that bonds such as family or community can deter deviant behaviours. In the interview, Jeremy mentioned that his father’s health deteriorated quickly and unfortunately passed away four months later.</p>

<p> These social breaks occurred once he realigned his behaviours to ensure that he could provide support for his family through proper education, and as a result, started attending school regularly and is now pursuing an undergraduate degree in a local university in Singapore. His personal loss and familial responsibility align closely with Hirschi’s theory which emphasises the importance of social ties and deterring deviance. </p>

@@

Well, the 10-year Compulsory Education Act has set an expectation for educational attainment, and would be considered deviant if one fails to comply. However, Jeremy’s journey through primary and secondary deviance illuminates the complexities of societal labelling and pressures. His experiences highlight the need to support reintegration over unproportionate measures, to foster a healthier school environment for all students.

>>>>

<summary>Singapore's Public Housing Affordability <br> <br> <p>In Singapore, housing affordability has become an increasing concern for future Singaporeans. However, in 2012, then-Deputy Prime Minister (DPM) Tharman Shanmugaratnam stated that a household income of SGD \$1,000 was sufficient to own a home, sparking discussions among netizens online (Tan, 2012). Read more here...</p></summary>

@@

While Mr. Tharman argued that housing grants could provide support for low-income households, many Singaporeans expressed concerns about the long-term viability of such claims, especially in the face of the constantly rising cost of living and property prices.

@@

This brings up a big question---will public housing in Singapore really stay affordable for the average Singaporean in the future? In this post, we\'ll take a closer look at how the housing market is evolving and what it could mean for future generations trying to own a home.

@@

We'll dive into the complexities of the housing market, analyze potential long-term trends, and explore how factors like estate, size, and remaining lease impact affordability. Ultimately, this analysis aims to identify the key factors that matter most.

@@

According to Kumar (2022), housing affordability in Singapore is a complex issue with many moving parts. The table above outlines current housing prices, offering a useful guide to understanding the financial commitment involved. Based on this data, it estimates the average salary each spouse would need to comfortably manage monthly repayments.

@@

For example, to afford a 3-room flat with a median price of \$360,000, both partners would need to earn at least SGD \$5,230 each. While this may seem manageable at first glance, it doesn\'t take into account other living expenses or potential income fluctuations. Couples may have additional financial commitments, such as owning a car or raising multiple children, which can significantly impact their overall affordability.

@@

magine you and your spouse are planning to start a family. Now that we\'ve taken a glimpse into the affordability of homes in Singapore, do you think you\'ll be able to comfortably own your own home when the time comes? Let\'s dive into the real data and explore this critical issue further.

@@

Before diving deeper into the analysis, let's first take a look at how housing prices have increased from 1990 to 2022. While the general upward trend in prices aligns with Singapore's economic growth, the rapid surge over this period is quite alarming.

@@

Some might argue that the rising prices are a reflection of a thriving economy. However, on the flip side, they also raise serious concerns about overall affordability. Now, let's take a closer look at the graph below to better understand the trends:

@@

The graph above shows a significant steepening in the trend of average resale prices in Singapore from 1990 to 2022, highlighting the sharp rise in housing costs across all flat types. The steeper slope in 2022 reflects a more pronounced price escalation compared to the 1990s. This trend could indicate growing pressure on affordability and an increasing financial strain for prospective homeowners.

@@

Notice on the graph that there\'s a concerning widening price gap between each successive flat type, with the difference in average prices becoming more pronounced over time. The jump in prices from a 3-room to a 4-room flat, both in 1990 and 2022, suggests a growing demand for larger homes. After all, a bigger home often means plans for a bigger family, right?

@@

With that in mind, the widening price gap could pose a significant financial burden for upgraders seeking more spacious accommodations for a growing family. This increasing disparity highlights the importance of careful planning when it comes to home ownership to avoid potential buyer's remorse in the future.

@@

Now, let\'s take a closer look at the price increases for each flat type individually across both years. The graph highlights a significant difference in the cost of a 4-room flat between 1990 and 2022. This stark contrast underscores how much prices have surged over the years, emphasizing the growing challenge of affordability for aspiring homeowners.

@@

In 1990, the average price of a 4-room flat was SGD \$81,525, while in 2022, it skyrocketed to SGD \$525,092---represented by green and orange markers on the graph, respectively. Check out the graph below to explore and compare the prices of other flat types between 1990 and 2022!

@@

As mentioned earlier, the rising trend in housing costs, as shown in the graph, suggests that potential homeowners may face significant financial barriers when searching for suitable housing options. Furthermore, the data indicates that the real estate market has become increasingly segmented over time. Unfortunately, with growing demand and limited supply, property agents are capitalizing on the eagerness of potential homebuyers (Lam, 2020).

@@

For instance, in 2019, a property agent was found guilty of engaging in unethical bidding practices to secure a higher commission (Lim, 2019). To address such issues, regulatory bodies must implement and enforce strict rules and guidelines to promote fair practices in this highly competitive and high-stakes market.

@@

While rising prices can signal affordability concerns, it\'s important to assess if they remain within a "safe" median range. However, the box plot below shows outliers that highlight significant and unprecedented price surges, raising concerns about long-term affordability.

@@

Furthermore, across other flat types, the increasing number of outliers beyond the upper whiskers of the 2022 box plots suggests substantial market growth. However, it also indicates a rising number of exceptional cases where resale prices are commanding even higher premiums---far exceeding already high median trends.

@@

Now that we've seen the high prices Singaporeans are willing to pay for their dream home, what other factors could be driving these increases? Next, we'll explore whether factors such as the remaining lease or the flat's location play a significant role in resale prices.

@@

To ease the financial burden, some flat upgraders may consider purchasing a flat with a shorter remaining lease. But does the remaining lease actually correlate with the resale flat prices in 1990 and 2022? Let's take a closer look at whether this factor influences affordability over time.

@@

As we dive into the numbers, it\'s clear that patterns have shifted significantly from 1990 to 2022. In this section, we\'ll compare data from these two distinct years to uncover key trends. Now, take a look at the scatterplot below---pay close attention to the red line. What does it reveal about the relationship between remaining lease and resale prices?

@@

In 1990, the trend was clear---a longer remaining lease often meant a higher resale price. The upward slope of the regression line was quite steep, indicating that buyers valued flats with longer leases, as they provided long-term security without lease expiration concerns.

@@

In 2022, while there's still a correlation, the slope is less steep, suggesting that the remaining lease is no longer as strong an indicator as it was in 1990. The data points are more spread out, showing greater variance in resale prices. This indicates that factors like location, flat type, and amenities have become more important than lease length in determining a flat's value.

@@

Put yourself in the buyer's shoes---would you prefer a flat with a longer remaining lease but located an hour away from everything, or a shorter lease with all the conveniences just a stone's throw away?

@@

The answer isn't just about counting the years left on a lease. So far, no HDB flat has reached the end of its lease, leaving uncertainty about what truly happens next. Buying a home is also about balancing the value of time and quality of life. After all, what's the point of a long lease if it comes at the expense of convenience and daily comfort? Now, let's dive into another crucial factor: the estate.

@@

Price is undoubtedly a major factor when purchasing a home, but have you decided where to live? Would you prefer to stay close to your parents in the same estate, or do you have a specific school in mind for your future children? Next, we'll explore how the estate impacts resale flat prices and identify which areas tend to be more expensive or budget-friendly for settling down.

@@

Now, let's explore the violin plot on the interactive dashboard, focusing on Bukit Timah and Punggol. According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is popular for its proximity to top schools like Hwa Chong Institution, National Junior College, and Raffles Girls' Primary School, making it a highly sought-after estate

@@

[Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate that\'s gaining popularity among younger couples. With modern amenities and promising development plans, it\'s being designed as an eco-friendly and sustainable town, offering trendy lifestyle hubs that cater to all age groups.</p>

With that in mind, let's analyze the violin plot. We can observe a wider distribution of resale prices, with a more pronounced upper tail. This suggests a greater variety of flats available, while also highlighting a substantial market for high-end luxury units.

@@

On the flip side, Punggol shows a narrower but denser concentration of prices, indicating less variation in resale prices. Now, go ahead and interact with the plot---select your dream estates and explore the price differences! And just in case, I've included the MRT map here for easy reference!

@@

Ultimately, deciding the best place to settle down depends on what matters most to you. If you prioritize tranquility and scenic sea views, Punggol might be the perfect fit.

@@

However, if being close to prestigious schools is your priority (yes, all schools are good schools---but let's not get into that), then Bukit Timah might be the better choice. These visualizations not only reveal price trends but also reflect lifestyle preferences and your long-term family vision.

@@

Year after year, resale HDB prices have continued to rise, reflecting the growing demand for housing in Singapore. However, this trend raises concerns for many Singaporeans, especially younger couples looking to start a family, as they face increasing challenges with affordability and availability.

@@

Recent reports indicate that analysts expect resale flat prices to rise moderately for the rest of 2023 (CNA, 2023). While cooling measures have been implemented to control prices, the growth observed in the third quarter of 2023 was driven by price resistance amid inflation and affordability concerns.

@@

You might be thinking, \*"Aren't there Build-to-Order (BTO) flats that are much cheaper with grants available?"\* And you're absolutely right! But are you ready to compete with tens of thousands of couples, wait 5-6 years, and still risk not getting a flat? Choosing to ballot for a BTO, despite its lower cost and grants, comes with its fair share of uncertainties and risks.

@@

This analysis offers a thoughtful evaluation of the need for immediate housing versus the potential delays and challenges of the BTO process. For now, the best approach is to make the most of available grants and focus on purchasing within our means.

@@

<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p>This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance. Read more here...</p></summary>

@@

Friday, 10 May 2024

@@

<p>Jeremy's desistance from deviance can be explored through Hirschi's (1969) Social Bond Theory. Kotlaja and Meier (2018), cited Hirschi (1969), mentioned that bonds such as family or community can deter deviant behaviours. In the interview, Jeremy mentioned that his father's health deteriorated quickly and unfortunately passed away four months later.</p>

<p>These social breaks occurred once he realigned his behaviours to ensure that he could provide support for his family through proper education, and as a result, started attending school regularly and is now pursuing an undergraduate degree in a local university in Singapore. His personal loss and familial responsibility align closely with Hirschi's theory which emphasises the importance of social ties and deterring deviance.</p>

@@

Well, the 10-year Compulsory Education Act has set an expectation for educational attainment, and would be considered deviant if one fails to comply. However, Jeremy's journey through primary and secondary deviance illuminates the complexities of societal labelling and pressures. His experiences highlight the need to support reintegration over unproportionate measures, to foster a healthier school environment for all students.

### 2025-01-24 index.qmd
2025 Update

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
> </blockquote>

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7238779076528442625" data-video-id="7238779076528442625" style="max-width: 605px;min-width: 325px;">

@@

<p>nha trang is my favvvvvv</p>

<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>

@@

# **My Past Work**

## National University of Singapore

### Social Thought and Theory

In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim. This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.

Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today. How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!

{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}

### Artificial Intelligence and Society

In this module, we looked at the benefits and potential downsides of relying on AI. My group focused on leveraging on AI technology to aid in bereavement process. I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with their loved ones - as an avatar!

![](docs/src/images/brochure.png)

### Design Thinking

In this module, we were assigned the task of innovating everyday chores. Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe!

![](images/prototyping.png){fig-align="center"}

The actual prototyping journey was not very smooth, but hey, here is the end product! Looks good aye? To me at least...

![](images/prototyping_2-01.png)

## Temasek Polytechnic

### Savvify - An Automated Savings Platform

During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***. Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.

Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!

{{< video https://youtu.be/kzWq31_mRyc >}}

### GIGAWipes - Innovation through Programming

"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives. This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but... I'll let the video do the talking...

{{< video https://youtu.be/2yBwaRCfiuI >}}

Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms

```         
```

>>>>

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">

@@

<p>errr i drank about 9 cups of pearl milk tea in 4 days 3 nights 🇹🇼🥴🧋🇹🇼</p>

<a target="_blank" title="♬ fish in the pool・花屋敷 - ヘクとパスカル" href="https://www.tiktok.com/music/fish-in-the-pool-花屋敷-6910585281334740994?refer=embed">♬ fish in the pool・花屋敷 - ヘクとパスカル</a>

@@

## Contact Details

For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com or visit my [LinkedIn Page](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)

### 2025-01-24 interests.qmd
update
update
2025 Update

---
title: "My Interests"
---

![](docs/src/images/soon.avif){width="730"}

>>>>

---
title: "My Past Work"
---

```{r, eval=TRUE,echo=FALSE}
```

## National University of Singapore

### Digital Storytelling

During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind. He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.

{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}

### Social Thought and Theory

In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim. This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.

Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today. How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!

{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}

### Artificial Intelligence and Society

In this module, we looked at the benefits and potential downsides of relying on AI. My group focused on leveraging on AI technology to aid in bereavement process. I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with their loved ones - as an avatar!

::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">

</iframe>
:::

<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>

### Temasek Polytechnic

### Savvify - An Automated Savings Platform

During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***. Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.

Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!

{{< video https://youtu.be/kzWq31_mRyc >}}

### GIGAWipes - Innovation through Programming

"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives. This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but... I'll let the video do the talking...

{{< video https://youtu.be/2yBwaRCfiuI >}}

Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms

```         
```

![](src/images/footer.png)
